\bf Causal Inference in Population Trends: Searching for Demographic Anomalies in Big Data

### 2020-08-03 MainDocument/MainDocument.tex
Updated.

The search for causality is one of the primary motiviations behind
social science \citep{smith2011commentary, pearl2009causal}. Causal
Inference, the identification of causal mechanisms, attempts to uncover
the underlying mechanisms that result in changes in a phenomenon and has
a long history as an approach to inquiry in the social sciences
\citep{grimmer2015ppsp}. Often, the identification of a casual mechanism
is accomplished via a randomized control trial (RCT) or expert knowledge
applied to a natural experiment \citep{salganik2019bit}.

Unfortunately, both RCTs and natural experiments have drawbacks. RCTs
are often prehibitively expensive for many scientists, precluding their
widespread adoption in the social sciences \citep{west2008ajph}. RCTs
are also sometimes impossible to deploy in the ``real world''. For
instance, an RCT to study country-level austeriy measures would be
difficult, if not impossible, to implement. Natural experiments are a
cheaper alternative, but provide less certainty about causation, fewer
opportunities to replicate work, and require expert knowledge of the
natural experiment to be properly employed \citep{pearl2018book}.

@@

In this paper, we combine a modern statistical outlier detection
algorithm \citep{chen1993joint}, abductive reasoning, and large
demographic data sets on more than 20 years of mortality/fertility to
identify anomalous demographic behavior. In essence, we identify
\emph{effects without knowledge of the cause}. We ask one fundamanetal
question regarding demographic anomalies: What are the hidden baby
booms/busts and mortality spikes/dips in the United States over the last
twenty years? We do not necessarily know the causes of these anomalies
but identifying them allows scientists with more detailed knowledge of
local population dynamics, state-level policy making, or macro-economics
to explain these phenomena post-hoc. From explanations of phenomena that
may have previously gone unnoticed, social scientists may be able to
better forecast populations and provide policy solutions for impending
problems such as climate change.

@@

We use a statistical time series outlier detection algorithm
\citep{chen1993joint}, implemented in the R programming language
\citep{rcore} via the tsoutliers package \citep{tsoutliers2019}. This
algorithm iteratively uses ARIMA models to 1) produce a counter-factual
time series to initially detect an outlier or anomaly, and 2) refit the
ARIMA with the outliers removed. Here we briefly summarize and describe
the method.

Often, the behavior of a time series can be described and summarized in
ARIMA models. If a series of values, \(y_t^*\), is subject to \(m\)
interventions or outliers at time points \(t_1,t_2,…,t_m\), then
\(y_t^*\) can be defined as

\[y_t^* = \sum_{j=1}^{m} \omega_jL_j(B)I_t(t_j) + \frac{\theta(B)}{\phi(B)\alpha(B)}\alpha_t\]

Where \(I_t(t_j)\) is an indicator variable with a value of 1 at
observation \(t_j\) and where the \(j\)th outlier arises, \(\phi(B)\) is
an autoregressive polynomial with all roots outside the unit circle,
\(\theta(B)\) is a moving average polynomial with all roots outside the
unit circle, and \(\alpha(B)\) is an autoregressive polynomial with all
roots on the unit circle.

We examine three types of outliers at time point \(t_m\): 1) additive
outliers (AO), defined as \(L_j(B)=1\); 2) level shift outliers (LS),
defined as \(L_j(B) = 1/(1-B)\); and 2) temporary change outliers (TC),
defined as \(L_j(B) = 1/(1-\delta B)\).

@@

An outlier is detected using a regression equation

\[ \pi(B)y_t^* \equiv \hat{e} = \sum_{j=1}^m \omega_j \pi(B)L_j(B)I_t(t_j) + \alpha_t \]

\begin{figure}
\centering
\includegraphics{./manuscript_files/figure-latex/Figure1.png}
\caption{\textbf{``Toy'' example of anomaly detection using the exchange
rate between the Euro and the Swiss Franc.} The Swiss Franc was pegged
to the Euro at 1.2 until January 15 2015 when the peg was removed and
the currency was allowed to trade more freely. This is a very strong
anomly in the time series (\emph{t}-stat = -144.07) detectable using
statistical methods and visually. The countefactural estimate with the
outlier removed would simply have kept the currency exchange at 1.2
(\(\hat{y}\)). \label{explanationfigure}}
\end{figure}

where \(\pi(B)=\sum_{i=o}^{inf} \pi_iB^i\). The identification of
outliers then involves a three step process. First, (1) the algorithm
identifies all potential outliers, \(t_j\) and \(L_j (B)\). Next, (2) we
compute joint estimates of model parameters and outlier effects to
identify potentially spurious outliers. Finally, (3) the outliers and
effects are re-estimated without spurious outliers. Of importance here
is step 2, which relies on some critical value above which an outlier at
time point \(m\) is considered spurious. Based on Chen and Liu's
\citeyearpar{chen1993joint} recommendation, we set a critical value of
3.5 which generally minimizes the possibility of Type I errors or false
positive outliers.

We report outliers using a simple t-statistic and report the size of the
outlier, or its impact on the time series, by subtracting \(\hat{y}\),
the adjusted time series with outliers removed, from \(y\), the
original, unadjusted time series.

@@

We detect numerous anomalous mortality and fertility events at the US
state-level since 1999. A full listing of these anomalies can be found
in the \textbf{Supplementary Materials}. We begin by highlighting
significant fertility and mortality anomaloies across all three types of
outliers (Additive Outliers, Level Shift Outliers, and Temporary Change
outliers) with plausible explanations. We then highlight two strong
anomalies that bely explanation. Finally, we conclude with a summary of
the anomalies we detect.

@@

We begin with a clear temporary change (TC) outlier for fertility in
Louisiana (\textbf{\autoref{fig:fertla}a}). Here we detect two TC
outliers, nearly back-to-back in 2005 (2005:08 \emph{t} = -6.002; and
2005:10 \emph{t} = -4.997), coinciding with the destruction of Hurricane
Katrina from the same year. The migration associated with Hurricane
Katrina has garnered most of the attention of social scientists
\citep{fussellRecoveryMigrationCity2014, horiDisplacementDynamicsSouthern2009},
but the hurricane had a very clear impact on fertility behaviors too,
creating a mini ``baby bust'' in Louisiana with the departure of many
people in their childbearing years. We estimate 4,411 fewer births in
Louisiana compared to the counterfactual, likely attributable to the
Hurricane.

We also highlight a level shift (LS) outlier for fertility in
Connecticut. Here we detect a strong (\emph{t}= -3.71 for -285
births/month) level shift toward lower fertility beginning in August
2009 (2009:08) that continues through the end of the period
(\textbf{\autoref{fig:fertla}b}). This LS toward lower fertility reduced
the number of births by 28,752 or 9\%) lower than the counterfactual
time series. The stock market crash of 2008, where the Dow Jones
Industrial Average had the largest single-day loss up to that point,
occurred just 11 months before we detect a shift toward lower fertility.
It is possible that the trend toward lower fertility in August 2009 and
the stock market crash in September 2008 are linked, although, as stated
previously, we are speculating only to illustrate how causal inference
could work in an abductive research agenda. A potentially interesting
future line of research would be to link fertility anomalies to the
kinds of economic shocks that may lead to outmigration of those in their
childbearing years.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/FertilityAnomalies-1.pdf}
\caption{\textbf{Anomaly detection in Louisiana (a) and Connecticut (b) state fertility, 2003-2018.}
The top part of each panel contains the original time series (light
gray), the corrected, counter-factual time series in the absence of
anomalies (blue), and the red dots correspond to the onset of detected
anomalies. The bottom part of each panel contains the magnitude and type
of the outlier in red. In (a), we detect two outliers, back-to-back,
likely resulting from Hurricane Katrina in August and October 2005,
representing a decrease of more than 4,400 births due to the hurricane
(t-statistics= -6.002 and -4.997). In (b), we detect one outlier, a
level shift outlier (LS) in August 2009. We believe this reduction is
attributable to the stock market crash 11 months earlier (t-statistic =
-3.71). \label{fig:fertla}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/MortalityAnomalies-1.pdf}
\caption{\textbf{Anomaly Detection for New York (a) and New Hampshire (b) state mortality, 1999-2016.}
In New York (a), we detect additive outliers (AO) in January 2000,
September 2001, January 2005, and January 2013; temporary change (TC)
outliers in February 2007 and January 2015; and a level shift (LS)
starting in February 2004. In New Hampshire (b), we detect two outliers,
both level shift outliers (LS) in April 2010 and again in November 2014.
These anomalies suggest New York experienced a significant mortality
event in September 2001 and New Hampshire experienced approximately
9,700 more deaths than expected since 2010 or 14\% more deaths in the
state over just seven years. \label{fig:mortnewhamp}}
\end{figure}

@@

This is contrast to \textbf{\autoref{fig:ferthawaii}b}, where we
identify a strange mortality reduction in Ohio (\emph{t}-stat: -4.27).
This LS is more than 1,157 deaths per month less than the counterfactual
time series, suggesting had nearly 40,000 fewer deaths since February
2015 than expected. This is the single-largest LS among all states. We
could not identify the potential policies Ohio might have put into place
to provide such a strong mortality protection.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/TrueAnomalies-1.pdf}
\caption{\textbf{Anomaly detection in Hawaii state fertility (a) and Ohio state mortality (b).}
Here we detect one outlier, an additive outlier (AO) in May 2014 in
Hawaii (a), representing a large, unexplainable 14\% increase in
expected births in that month. We also detect a strong level shift (LS)
reduction (b), representing a large, unexplainable reduction of nearly
40,000 deaths in Ohio. \label{fig:ferthawaii}}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-6}\textbf{Summary by Demographic Component.}  Here we can see there 22 Fertility and 156 Mortality anomalies among the state-level time series, totalling more than 200k anomalous births and 600k anomalous deaths. \label{sumtable}}
\centering
\begin{tabular}[t]{lrllrrr}
\toprule
Component & Anomalies & $y$ & $\hat{y}$ & $y-\hat{y}$ & $|y-\hat{y}|$ & \% of Total\\
\midrule
Fertility & 22 & 25.48M & 25.68M & -202,217 & 226,476 & 0.889\\
Mortality & 156 & 43.57M & 43.52M & 48,535 & 627,364 & 1.440\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/AnomalyMap-1.pdf}
\caption{\textbf{Summary of Anomalies by type, demographic component, and State.}
We observe much fewer fertility anomalies than mortality anomalies.
\label{fig:summap}}
\end{figure}

@@

In this paper, we show how the tsoutlier package in R can be implemented
to conduct statistical time series outlier detection, an inductive
approach that aids in the creation of deductive reasoning. This
algorithm is one of many causal inference approaches that are freely and
commercially available (see \citet{rcausalimpact}). In our initial work,
we experimented with other approaches, such as Google's causalimpact
algorithm, which uncovered the same patterns we briefly discuss in this
paper. By making more use of causal inference techniques and abductive
modeling approaches, we argue that social scientists will be able to
better understand how events or policy implementation can impact
important outcomes. For example, we could uncover---on a wide
scale---how gun control policies may reduce or increase injuries from
shootings or how marijuana legalization might impact opioid deaths. We
could also uncover how increases in extreme weather events impact a
range of behaviors such as home sales, bottled water purchases, and even
fertility.

@@

\bibliographystyle{agsm}
\bibliography{mybibfile}

>>>>

The search for causality is one of the primary motivations behind social
science \citep{smith2011commentary, pearl2009causal}. Causal Inference,
the identification of causal mechanisms, attempts to uncover the
underlying mechanisms that result in changes in a phenomenon and has a
long history as an approach to inquiry in the social sciences
\citep{grimmer2015ppsp}. Often, the identification of a casual mechanism
is accomplished via a randomized control trial (RCT) or expert knowledge
applied to a natural experiment \citep{salganik2019bit}.

Unfortunately, both RCTs and natural experiments have drawbacks. RCTs
are often prohibitively expensive for many scientists, precluding their
widespread adoption in the social sciences \citep{west2008ajph}. RCTs
are also sometimes impossible to deploy in the ``real world''. For
instance, an RCT to study country-level austerity measures would be
difficult, if not impossible, to implement. Natural experiments are a
cheaper alternative, but provide less certainty about causation, fewer
opportunities to replicate work, and require expert knowledge of the
natural experiment to be properly employed \citep{pearl2018book}.

@@

In this paper, we combine a modern statistical outlier detection
algorithm \citep{chen1993joint}, abductive reasoning, and large
demographic data sets on more than 20 years of mortality/fertility to
identify anomalous demographic behavior. In essence, we identify
\emph{effects without knowledge of the cause}. We ask one fundamental
question regarding demographic anomalies: What are the hidden baby
booms/busts and mortality spikes/dips in the United States over the last
twenty years? We do not necessarily know the causes of these anomalies
but identifying them allows scientists with more detailed knowledge of
local population dynamics, state-level policy making, or macro-economics
to explain these phenomena post-hoc. From explanations of phenomena that
may have previously gone unnoticed, social scientists may be able to
better forecast populations and provide policy solutions for impending
problems such as climate change.

@@

We use a statistical time series outlier detection algorithm
\citep{chen1993joint}, implemented in the R programming language
\citep{rcore} via the tsoutliers package \citep{tsoutliers2019}. This
algorithm iteratively uses ARIMA models to 1) identify potential
outliers or anomalies and 2) refit the ARIMA with the outliers removed
to produce a counter-factual time series. Here we briefly summarize and
describe the method.

Often, the behavior of a time series can be described and summarized in
ARIMA models. If a series of values, \(y_t^*\), is subject to \(m\)
interventions or outliers at time points \(t_1,t_2,…,t_m\) with weights
\(\omega\) then \(y_t^*\) can be defined as

\begin{equation}
\label{eq:arima}
y_t^* = \sum_{j=1}^{m} \omega_jL_j(B)I_t(t_j) + \frac{\theta(B)}{\phi(B)\alpha(B)}\alpha_t 
\end{equation}

Where \(I_t(t_j)\) is an indicator variable with a value of 1 at
observation \(t_j\) and where the \(j\)th outlier arises,\\
\(\phi(B)\) is an autoregressive polynomial with all roots outside the
unit circle,\\
\(\theta(B)\) is a moving average polynomial with all roots outside the
unit circle,\\
and \(\alpha(B)\) is an autoregressive polynomial with all roots on the
unit circle.

We examine three types of outliers at time point \(t_m\):\\
1. additive outliers (AO), defined as \(L_j(B)=1\);\\
2. level shift outliers (LS), defined as \(L_j(B) = 1/(1-B)\); and\\
3. temporary change outliers (TC), defined as
\(L_j(B) = 1/(1-\delta B)\) where \(\delta\) is equal to 0.7.

@@

An outlier is detected with the estimated residuals using a regression
equation

\begin{equation}
\label{eq:residuals}
\pi(B)y_t^* \equiv \hat{e} = \sum_{j=1}^m \omega_j \pi(B)L_j(B)I_t(t_j) + \alpha_t
\end{equation} where \(\pi(B)=\sum_{i=o}^{inf} \pi_iB^i\).

Equations \ref{eq:arima} and \ref{eq:residuals} allow for an automatic
detection of anomalies iterated over a two-stage process.

In stage 1, anomalies are located. First, an ARIMA model is fit to the
time series using the \texttt{forecast} package in R
\citep{Rforecast, hymdman2008} where the best performing ARIMA model is
selected based on the Bayesian information criterion (BIC). Next, the
residuals from the forecast are checked for their significance using
equation \ref{eq:residuals} where only anomalies above a critical
\emph{t}-static are considered ``true'' anomalies (\(|\tau| \geq 3.5\)).
We choose this critical value based on Chen and Liu's
\citeyearpar{chen1993joint} recommendation to minimize Type I or
false-positive anomalies. Finally, two additional rules are implemented:
If multiple anomalies are detected at the same time point, only the most
significant anomaly is selected and if anomalies of the same type at
consecutive time periods are detected, only the anomaly with highest
\emph{t}-statistic is selected.

In stage 2, anomalies are removed from the time series and a new ARIMA
model is chosen and fit. The selection of the initial ARIMA model could
have been affected by the presence of the anomalies, making some
anomalies spuriously identified. To correct for this, a new ARIMA model
is fit accounting for additional regression effects in equation
\ref{eq:arima} from the list of candidate anomalies identified in stage
1, effectively removing the anomalies from the time series. Each anomaly
is then reassessed under the new model and those anomalies that are no
longer significant are removed.

These two stages are then iterated until no additional anomalies are
detected.

\hypertarget{robustness-check}{%
\subsection{Robustness Check}\label{robustness-check}}

To determine the false-positive (Type I) and false-negative (Type II)
error rates under a critical value of 3.5, we ran two simulations. For
the false-positive error we simulated 1000 time series with 180 time
steps without introducing any anomalies and ran the \texttt{tsoutliers}
algorithm on them. Any anomalies we detect in these time series are
spurious anomalies. For the false-negative error, we simulated 1000 time
series with 180 time steps but introduced a single anomaly of the same
magnitude at the same time point in each time series. If the
\texttt{tsoutliers} algorithm fails to detect the anomaly, it would be
considered a false-negative error.

In our anomaly-less time series, we detect 208 anomalies on the 180,000
candidate time steps for a false-positive error rate of 0.116\%. In our
time series containing a single anomaly, we detect 817 anomalies out of
the 1000 candidate time series, for a false-negative error rate of
18.3\%. This provides a statistical power of 0.817. These results give
us confidence that the anomalies we detect in this paper are true
anomalies.

\begin{figure}
\centering
\includegraphics{../MainDocument/MainDocument_files/figure-latex/Figure1.png}
\caption{\textbf{``Toy'' example of anomaly detection using the exchange
rate between the Euro and the Swiss Franc.} The Swiss Franc was pegged
to the Euro at 1.2 until January 15 2015 when the peg was removed and
the currency was allowed to trade more freely. This is a very strong
anomly in the time series (\emph{t}-stat = -144.07) detectable using
statistical methods and visually. The countefactural estimate with the
outlier removed would simply have kept the currency exchange at 1.2
(\(\hat{y}\)). \label{explanationfigure}}
\end{figure}

\hypertarget{toy-example}{%
\subsection{Toy example}\label{toy-example}}

@@

We detect numerous anomalous mortality and fertility events at the US
state-level since 1999. A full listing of these anomalies can be found
in the \textbf{Supplementary Materials}. We begin by highlighting
significant fertility and mortality anomalies across all three types of
outliers (Additive Outliers, Level Shift Outliers, and Temporary Change
outliers) with plausible explanations. We then highlight two strong
anomalies that bely explanation. Finally, we conclude with a summary of
the anomalies we detect.

@@

We begin with a clear temporary change (TC) outlier for fertility in
Louisiana (\textbf{\autoref{fig:fertla}a}). Here we detect two TC
outliers, nearly back-to-back in 2005 (2005:08 \emph{t} = -6.002; and
2005:10 \emph{t} = -4.997), coinciding with the destruction of Hurricane
Katrina from the same year. The migration associated with Hurricane
Katrina has garnered most of the attention of social scientists
\citep{fussellRecoveryMigrationCity2014, horiDisplacementDynamicsSouthern2009},
but the hurricane had a very clear impact on fertility behaviors too,
creating a mini ``baby bust'' in Louisiana with the departure of many
people in their childbearing years. We estimate 4,411 fewer births in
Louisiana compared to the counter-factual, likely attributable to the
Hurricane.

We also highlight a level shift (LS) outlier for fertility in
Connecticut. Here we detect a strong (\emph{t}= -3.71 for -285
births/month) level shift toward lower fertility beginning in August
2009 (2009:08) that continues through the end of the period
(\textbf{\autoref{fig:fertla}b}). This LS toward lower fertility reduced
the number of births by 28,752 or 9\%) lower than the counter-factual
time series. The stock market crash of 2008, where the Dow Jones
Industrial Average had the largest single-day loss up to that point,
occurred just 11 months before we detect a shift toward lower fertility.
It is possible that the trend toward lower fertility in August 2009 and
the stock market crash in September 2008 are linked, although, as stated
previously, we are speculating only to illustrate how causal inference
could work in an abductive research agenda. A potentially interesting
future line of research would be to link fertility anomalies to the
kinds of economic shocks that may lead to out-migration of those in
their childbearing years.

\begin{figure}
\centering
\includegraphics{MainDocument_files/figure-latex/FertilityAnomalies-1.pdf}
\caption{\textbf{Anomaly detection in Louisiana (a) and Connecticut (b) state fertility, 2003-2018.}
The top part of each panel contains the original time series (light
gray), the corrected, counter-factual time series in the absence of
anomalies (blue), and the red dots correspond to the onset of detected
anomalies. The bottom part of each panel contains the magnitude and type
of the outlier in red. In (a), we detect two outliers, back-to-back,
likely resulting from Hurricane Katrina in August and October 2005,
representing a decrease of more than 4,400 births due to the hurricane
(t-statistics= -6.002 and -4.997). In (b), we detect one outlier, a
level shift outlier (LS) in August 2009. We believe this reduction is
attributable to the stock market crash 11 months earlier (t-statistic =
-3.71). \label{fig:fertla}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{MainDocument_files/figure-latex/MortalityAnomalies-1.pdf}
\caption{\textbf{Anomaly Detection for New York (a) and New Hampshire (b) state mortality, 1999-2016.}
In New York (a), we detect additive outliers (AO) in January 2000,
September 2001, January 2005, and January 2013; temporary change (TC)
outliers in February 2007 and January 2015; and a level shift (LS)
starting in February 2004. In New Hampshire (b), we detect two outliers,
both level shift outliers (LS) in April 2010 and again in November 2014.
These anomalies suggest New York experienced a significant mortality
event in September 2001 and New Hampshire experienced approximately
9,700 more deaths than expected since 2010 or 14\% more deaths in the
state over just seven years. \label{fig:mortnewhamp}}
\end{figure}

@@

This is contrast to \textbf{\autoref{fig:ferthawaii}b}, where we
identify a strange mortality reduction in Ohio (\emph{t}-stat: -4.27).
This LS is more than 1,157 deaths per month less than the
counter-factual time series, suggesting had nearly 40,000 fewer deaths
since February 2015 than expected. This is the single-largest LS among
all states. We could not identify the potential policies Ohio might have
put into place to provide such a strong mortality protection.

\begin{figure}
\centering
\includegraphics{MainDocument_files/figure-latex/TrueAnomalies-1.pdf}
\caption{\textbf{Anomaly detection in Hawaii state fertility (a) and Ohio state mortality (b).}
Here we detect one outlier, an additive outlier (AO) in May 2014 in
Hawaii (a), representing a large, unexplainable 14\% increase in
expected births in that month. We also detect a strong level shift (LS)
reduction (b), representing a large, unexplainable reduction of nearly
40,000 deaths in Ohio. \label{fig:ferthawaii}}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-7}\textbf{Summary by Demographic Component.}  Here we can see there 22 Fertility and 156 Mortality anomalies among the state-level time series, totalling more than 200k anomalous births and 600k anomalous deaths. \label{sumtable}}
\centering
\begin{tabular}[t]{lrllrrr}
\toprule
Component & Anomalies & $y$ & $\hat{y}$ & $y-\hat{y}$ & $|y-\hat{y}|$ & \% of Total\\
\midrule
Fertility & 22 & 25.48M & 25.68M & -202,217 & 226,476 & 0.889\\
Mortality & 156 & 43.57M & 43.52M & 48,535 & 627,364 & 1.440\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{MainDocument_files/figure-latex/AnomalyMap-1.pdf}
\caption{\textbf{Summary of Anomalies by type, demographic component, and State.}
We observe much fewer fertility anomalies than mortality anomalies.
\label{fig:summap}}
\end{figure}

@@

In this paper, we show how the tsoutlier package in R can be implemented
to conduct statistical time series outlier detection, an inductive
approach that aids in the creation of deductive reasoning. This
algorithm is one of many causal inference approaches that are freely and
commercially available (see \citet{rcausalimpact}). In our initial work,
we experimented with other approaches, such as Google's CausalImpact
algorithm, which uncovered the same patterns we briefly discuss in this
paper. By making more use of causal inference techniques and abductive
modeling approaches, we argue that social scientists will be able to
better understand how events or policy implementation can impact
important outcomes. For example, we could uncover---on a wide
scale---how gun control policies may reduce or increase injuries from
shootings or how marijuana legalization might impact opioid deaths. We
could also uncover how increases in extreme weather events impact a
range of behaviors such as home sales, bottled water purchases, and even
fertility.

@@

\bibliographystyle{agsm}
\bibliography{../MainDocument/mybibfile.bib}
